\documentclass[12pt,fleqn]{book}

\usepackage{titlesec}
\usepackage{caption}

\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries}{}{0pt}{\Huge}
\titlespacing{\chapter}
  {0pt}{10pt}{40pt}

\usepackage{amsmath,amssymb,amsfonts,graphicx,tasks,tikz,pgfplots}
\usetikzlibrary{arrows}
\pgfplotsset{compat=1.17}

\usepackage{tasks}
\settasks{
  label-width = 18pt
}
 
\makeatletter
 \def\@textbottom{\vskip \z@ \@plus 1pt}
 \let\@texttop\relax
\makeatother

\usepackage[letterpaper,margin=0.5in,footskip=.5cm]{geometry}

\input{../math-defs.tex}

\pagestyle{plain}
\usepackage[lastexercise,answerdelayed]{exercise}
\usepackage{totcount}
\regtotcounter{Exercise} % register the counter for getting the total
\usepackage{chngcntr}
\counterwithin{Exercise}{chapter}
\counterwithin{Answer}{chapter}
\usepackage{xassoccnt}
\NewTotalDocumentCounter{totalex}
\usepackage{titleref}
\usepackage{etoolbox}

%EXERCISE START

\renewcommand{\ExerciseHeader}{ \stepcounter{totalex}\ifnumcomp{\value{Exercise}}{=}{1}{\ifnumcomp{\thechapter}{=}{1}{}{\vspace{10pt}}\noindent\Large\textbf{Exercises}\par\vspace{10pt}}{}\noindent\normalsize\bfseries\ExerciseHeaderNB\ExerciseHeaderDifficulty.}
\renewcommand{\AnswerHeader}{\ifnumcomp{\value{Exercise}}{=}{1}{\ifnumcomp{\thechapter}{=}{1}{}{\vspace{10pt}}\noindent\Large\textbf{Section\ \thechapter\ Solutions}\par\vspace{10pt}}{}\noindent\normalsize\bfseries\ExerciseHeaderNB.\ }

\usepackage{hyperref}

\newcommand{\prb}[1]{\begin{Exercise}#1\end{Exercise}}
\newcommand{\sol}[1]{\begin{Answer}#1\end{Answer}}

%EXERCISE END



\begin{document}
\noindent
\thispagestyle{empty}
Grade 10 Advanced Math \hfill Name: \hspace{2in}
\medskip\hrule
\noindent

\vfill

\begin{center}
	{\bf \huge Chapter 3: Radicals and Exponents}
\end{center}

\vfill
\vfill

\clearpage

\setcounter{page}{1}

{\bf \huge Introduction }
\\[1in]
In the first chapter, we dealt with functions that could be sketched as a straight line.  We observed how they intersected with each other, and how we can use algebra to describe those intersections.
\\[1em]
In the second chapter, we learned about polynomial functions, namely quadratics, and how they can be graphed.  We spent a great deal of time finding roots of a quadratic, and even learned about imaginary numbers.
\\[1em]
In this chapter, we will learn about the inverse of a quadratic -- a radical.  We will learn how to play with these kinds of numbers, what \emph{kinds} of numbers they can be, and how to express them in various ways.
\\[1em]
Try this warm up to see if you can get all of these facts right.
\begin{tasks}(2)
    \task $3^2=$
    \task $(-3)^2=$
    \\[1em]
    \task If $x^2=9,$ then $x=$
    \task $\sqrt 9 =$
    \\[1em]
    \task $\sqrt{x^2}=$
    \task $(\sqrt x)^2=$
\end{tasks}
\clearpage
\chapter{1. Relations, Functions, One-to-one}
\chapter{2. Inverse Functions}
\chapter{3. The Radical Function}
\chapter{4. Number Systems}
\chapter{5. Manipulating Radicals}
\chapter{6. Factoring}
\chapter{7. Exponential Notation}
\prb{a problem}
\sol{a solution}
\chapter{Selected Solutions.}
\shipoutAnswer
\end{document}
